Template for indicator documentation

### 2023-09-14 slitasje.Rmd
Change indicator name and add vertical line in figure

# Slitasje og kjørespor {#slitasje}

@@

March 2023

@@

```{r dense-stats, fig.height= 12, fig.cap="Barplot showing the number of data points, the area weighted indicator values and the sd for the slitasje indicator. Transparrent bars represents categories with less than 150 data points."}
temp_plot <- all_stats %>%
  mutate(HIF_NA = case_when(
    n > 150 ~ HIF
  ))

@@

ggarrange(
ggplot(temp_plot, aes(x = region, y = n, group = HIF, fill = HIF_NA))+
  geom_bar(position = "dodge", stat = "identity", col="black")+
  theme_bw(base_size = 10)+
  scale_fill_brewer(palette="Oranges")+
  theme(axis.text.x = element_text(angle = 90, vjust=0.5))+
  coord_flip()+
  facet_wrap(.~eco),
ggplot(temp_plot, aes(x = region, y = w_mean, group = HIF, fill = HIF_NA))+
  geom_bar(position = "dodge", stat = "identity", col="black")+
  theme_bw(base_size = 10)+
  scale_fill_brewer(palette="Oranges")+
  theme(axis.text.x = element_text(angle = 90, vjust=0.5))+
  coord_flip()+
  facet_wrap(.~eco),
ggplot(temp_plot, aes(x = region, y = sd, group = HIF, fill = HIF_NA))+
  geom_bar(position = "dodge", stat = "identity", col="black")+
  theme_bw(base_size = 10)+
  scale_fill_brewer(palette="Oranges")+
  theme(axis.text.x = element_text(angle = 90, vjust=0.5))+
  coord_flip()+
  facet_wrap(.~eco),
ncol = 1)

@@

```{r extrapolated-slitasje, fig.cap="Slitasje indicator extrapolated over Trondheim, with one map for each ecosystem. The map is not masked against ecosystem delineation maps, which make them easy to missinterpret."}
myCol <- "RdYlGn"
tmap_arrange(
tm_shape(wetlands_slitasje_extr_trd)+
  tm_polygons(col = "w_mean",
    title="Slitasje indicator",
    palette = myCol,
    style="cont",
    breaks = c(0,1))+
  tm_layout(legend.outside = T)+
  tm_shape(hw_utm)+
  tm_lines(col="blue")+
  tm_layout(title = "Wetland"),

tm_shape(seminat_slitasje_extr_trd)+
  tm_polygons(col = "w_mean",
    title="Slitasje indicator",
    palette = myCol,
    style="cont",
    breaks = c(0,1))+
  tm_layout(legend.outside = T)+
  tm_shape(hw_utm)+
  tm_lines(col="blue")+
  tm_layout(title = "Semi-natural areas"),

tm_shape(natOpen_slitasje_extr_trd)+
  tm_polygons(col = "w_mean",
    title="Slitasje indicator",
    palette = myCol,
    style="cont",
    breaks = c(0,1))+
  tm_layout(legend.outside = T)+
  tm_shape(hw_utm)+
  tm_lines(col="blue")+
  tm_layout(title = "Naturally open areas"),
HIA_trd)
```

@@

### Slitasje in wetlands

>>>>

# Anthropogenic disturbance to soils and vegetation ADSV {#slitasje}

@@

September 2023

Norwegian indicator name: Slitasje

@@

```{r dense-stats, fig.height= 12, fig.cap="Barplot showing the number of data points, the area weighted scaled indicator values and the sd for the ADSV indicator. Transparent bars represents categories with less than 150 data points, indicated by the vertical line in the top row of panes."}
temp_plot <- all_stats %>%
  mutate(HIF_NA = case_when(
    n > 150 ~ HIF
  ))

@@

ggarrange(
ggplot(temp_plot, aes(x = region, y = n, group = HIF, fill = HIF_NA))+
  geom_bar(position = "dodge", stat = "identity", col="black")+
  theme_bw(base_size = 10)+
  scale_fill_brewer(palette="Oranges", na.translate=F)+
  theme(axis.text.x = element_text(angle = 90, vjust=0.5))+
  coord_flip()+
  labs(fill = "HIF")+
  geom_hline(yintercept=150)+
  facet_wrap(.~eco),
ggplot(temp_plot, aes(x = region, y = w_mean, group = HIF, fill = HIF_NA))+
  geom_bar(position = "dodge", stat = "identity", col="black")+
  theme_bw(base_size = 10)+
  scale_fill_brewer(palette="Oranges",  na.translate=F)+
  theme(axis.text.x = element_text(angle = 90, vjust=0.5))+
  coord_flip()+
  labs(fill = "HIF")+
  facet_wrap(.~eco),
ggplot(temp_plot, aes(x = region, y = sd, group = HIF, fill = HIF_NA))+
  geom_bar(position = "dodge", stat = "identity", col="black")+
  theme_bw(base_size = 10)+
  scale_fill_brewer(palette="Oranges",  na.translate=F)+
  theme(axis.text.x = element_text(angle = 90, vjust=0.5))+
  coord_flip()+
  labs(fill = "HIF")+
  facet_wrap(.~eco),
ncol = 1)

@@

```{r extrapolated-slitasje, fig.cap="ADSV indicator extrapolated over Trondheim, with one map for each ecosystem. The map is not masked against ecosystem delineation maps, which make them easy to missinterpret."}
myCol <- "RdYlGn"
tmap_arrange(
tm_shape(wetlands_slitasje_extr_trd)+
  tm_polygons(col = "w_mean",
    title="Indicator value",
    palette = myCol,
    style="cont",
    breaks = c(0,1))+
  tm_layout(legend.outside = T)+
  tm_shape(hw_utm)+
  tm_lines(col="blue")+
  tm_layout(title = "Wetland"),

tm_shape(seminat_slitasje_extr_trd)+
  tm_polygons(col = "w_mean",
    title="Indicator value",
    palette = myCol,
    style="cont",
    breaks = c(0,1))+
  tm_layout(legend.outside = T)+
  tm_shape(hw_utm)+
  tm_lines(col="blue")+
  tm_layout(title = "Semi-natural areas"),

tm_shape(natOpen_slitasje_extr_trd)+
  tm_polygons(col = "w_mean",
    title="Indicator value",
    palette = myCol,
    style="cont",
    breaks = c(0,1))+
  tm_layout(legend.outside = T)+
  tm_shape(hw_utm)+
  tm_lines(col="blue")+
  tm_layout(title = "Naturally open areas"),
HIA_trd)
```

@@

### ADSV in wetlands
